---
title: "SMB_DADI_ANALYSIS"
author: "Joe Gunn"
date: "5/18/2021"
output: html_document
---

# Libraries needed for analysis
```{r setup, include=FALSE}
library(genepopedit)
library(parallelnewhybrid)
library(hybriddetective)
library(readxl)
library(tidyverse)
library(cowplot)
library(pophelper)
library(tools)
```

#Explanation of dadi analysis

I am running the program DADI using python3 within the Anaconda3 python environment. All of the models I am running are based on 2D folded joint frequency spectra, and the python scripts for each model have all been previously published in the Two_Population_Pipeline within the dadi_pipeline written by Daniel Portik and KC Charles (see below for citations). The two epoch diversification models I have selected were developed by KC Charles, while all of the rest of the models were developed by D. Portik.

To run all models, I adapted the dadi_Run_2D_Set.py python script provided in the dadi_pipeline. I converted vcf files for each pair of populations for analysis directly in the script using the code for coverting a vcf to an fs spectrum object. For each pair of populations, I projected to the exact number of alleles expected in each set of individuals (2*the number of individuals, because diploid). This is because I used the vcf2sfs.r script (see SMB_DADI_PREP.Rmd) to impute missing genotype values based on the binomical distribution. Thus, for each pair of populations, I retained the maximum number of segregating sites (SNPS) with complete data.

I am modeling the demographic history between four pairs of populations:

  1. Elk River (ELK) and White River (WHITE)
  2. Bayou River (BAYOU) and White River (WHITE)
  3. Upper Arkansas Tributaries (UPPARK) and the White River (WHITE)
  4. Illinois River (ILLI) and Skiatook Lake (SKIA)
  
I am running 9 independent demographic models on these four population pairs: 

  1. no_mig: Divergence with no migration
  2. sym_mig: Divdergence with continuous symmetric migration
  3. asym_mig: Divergence with continuous asymmetric migration
  4. sec_contact_sym_mig: Divergence in isolation, continuous symmetric secondary contact (recent symmetric admixture)
  5. sec_contact_asym_mig: Divergence in isolation, continuous asymmetric secondary contact (recent asymmetric admixture)
  6. anc_sym_mig: Divergence with ancient continuous symmetric migration, then isolation (ancient symmetric admixture)
  7. anc_asym_mig: Divergence with ancient continuous asymmetric migration, then isolation (ancient asymmetric admixture)
  8. sym_mig_twoepoch: Divergence with continuous symmetric migration that varies across two epochs
  9. asym_mig_twoepoch: Divergence with continuous asymmetric migration that varies across two epochs


Citation information:

Portik, D.M., Leache, A.D., Rivera, D., Blackburn, D.C., Rodel, M.-O.,
    Barej, M.F., Hirschfeld, M., Burger, M., and M.K. Fujita. 2017.
    Evaluating mechanisms of diversification in a Guineo-Congolian forest
    frog using demographic model selection. Molecular Ecology 26: 5245-5263.
    doi: 10.1111/mec.14266
    
Charles, K.C., Bell, R.C., Blackburn, D.C., Burger, M., Fujita, M.K.,
    Gvozdik, V., Jongsma, G.F.M., Leache, A.D., and D.M. Portik. Sky, sea,
    and forest islands: diversification in the African leaf-folding frog
    Afrixalus paradorsalis (Order: Anura, Family: Hyperoliidae).
    Journal of Biogeography 45: 1781-1794. 
    doi: 10.1111/jbi.13365
    
## Convert txt files into usable dataframes
```{r}

#ELK and WHITE
files_elk <- list.files(path="../dadi_analysis/analysis/text_file_results/elk_white/diversification_models_neutral_snps", pattern="*.optimized.txt", full.names=F, recursive=FALSE)

files1_elk <- list.files(path="../dadi_analysis/analysis/text_file_results/elk_white/diversification_models_neutral_snps", pattern="*.optimized.txt", full.names=T, recursive=FALSE)


csv_file_names_elk <- file_path_sans_ext(files_elk)
all_files_elk <- lapply(files1_elk, FUN=read.table, header=T, sep="\t")

for (i in 1:length(files_elk)) {
  t <- all_files_elk[[i]]
    t_split <- t %>%
      separate(Replicate, 
               sep="_", 
               remove=TRUE, 
               into=c("Round_col","Round","Rep_col","Replicate"))
    t_split_remove <- t_split[,-c(2,4)]
    t_split_remove_2 <- t_split_remove[,-c(8)]
    
    df <- as.data.frame(t_split_remove_2) # load file
    df_clean <- df %>%
      mutate(Model = factor(Model), 
             Round = factor(Round)) 

    write.csv(df_clean, file=paste0("../dadi_analysis/analysis/text_file_results/elk_white/diversification_models_neutral_snps/", csv_file_names_elk[i], ".csv"))
}

#BAYOU and WHITE
files_bayou <- list.files(path="../dadi_analysis/analysis/text_file_results/bayou_white/diversification_models_neutral_snps", pattern="*.optimized.txt", full.names=F, recursive=FALSE)

files1_bayou <- list.files(path="../dadi_analysis/analysis/text_file_results/bayou_white/diversification_models_neutral_snps", pattern="*.optimized.txt", full.names=T, recursive=FALSE)


csv_file_names_bayou <- file_path_sans_ext(files_bayou)
all_files_bayou <- lapply(files1_bayou, FUN=read.table, header=T, sep="\t")

for (i in 1:length(files_bayou)) {
  t <- all_files_bayou[[i]]
    t_split <- t %>%
      separate(Replicate, 
               sep="_", 
               remove=TRUE, 
               into=c("Round_col","Round","Rep_col","Replicate"))
    t_split_remove <- t_split[,-c(2,4)]
    t_split_remove_2 <- t_split_remove[,-c(8)]
    
    df <- as.data.frame(t_split_remove_2) # load file
    df_clean <- df %>%
      mutate(Model = factor(Model), 
             Round = factor(Round)) 

    write.csv(df_clean, file=paste0("../dadi_analysis/analysis/text_file_results/bayou_white/diversification_models_neutral_snps/", csv_file_names_bayou[i], ".csv"))
}

#UPPARK and WHITE
files_uppark <- list.files(path="../dadi_analysis/analysis/text_file_results/uppark_white/diversification_models_neutral_snps", pattern="*.optimized.txt", full.names=F, recursive=FALSE)

files1_uppark <- list.files(path="../dadi_analysis/analysis/text_file_results/uppark_white/diversification_models_neutral_snps", pattern="*.optimized.txt", full.names=T, recursive=FALSE)


csv_file_names_uppark <- file_path_sans_ext(files_uppark)
all_files_uppark <- lapply(files1_uppark, FUN=read.table, header=T, sep="\t")

for (i in 1:length(files_uppark)) {
  t <- all_files_uppark[[i]]
    t_split <- t %>%
      separate(Replicate, 
               sep="_", 
               remove=TRUE, 
               into=c("Round_col","Round","Rep_col","Replicate"))
    t_split_remove <- t_split[,-c(2,4)]
    t_split_remove_2 <- t_split_remove[,-c(8)]
    
    df <- as.data.frame(t_split_remove_2) # load file
    df_clean <- df %>%
      mutate(Model = factor(Model), 
             Round = factor(Round)) 

    write.csv(df_clean, file=paste0("../dadi_analysis/analysis/text_file_results/uppark_white/diversification_models_neutral_snps/", csv_file_names_uppark[i], ".csv"))
}

#ILLI and SKIA
files_illi <- list.files(path="../dadi_analysis/analysis/text_file_results/illi_skia/diversification_models_neutral_snps", pattern="*.optimized.txt", full.names=F, recursive=FALSE)

files1_illi <- list.files(path="../dadi_analysis/analysis/text_file_results/illi_skia/diversification_models_neutral_snps", pattern="*.optimized.txt", full.names=T, recursive=FALSE)


csv_file_names_illi <- file_path_sans_ext(files_illi)
all_files_illi <- lapply(files1_illi, FUN=read.table, header=T, sep="\t")

for (i in 1:length(files_illi)) {
  t <- all_files_illi[[i]]
    t_split <- t %>%
      separate(Replicate, 
               sep="_", 
               remove=TRUE, 
               into=c("Round_col","Round","Rep_col","Replicate"))
    t_split_remove <- t_split[,-c(2,4)]
    t_split_remove_2 <- t_split_remove[,-c(8)]
    
    df <- as.data.frame(t_split_remove_2) # load file
    df_clean <- df %>%
      mutate(Model = factor(Model), 
             Round = factor(Round)) 

    write.csv(df_clean, file=paste0("../dadi_analysis/analysis/text_file_results/illi_skia/diversification_models_neutral_snps/", csv_file_names_illi[i], ".csv"))
}

```

# DADI Optimization

## DIVERSIFICATION MODELS

## ELK and WHITE 
```{r}
#MODEL 1: NO_MIG
elk_white_no_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/elk_white/diversification_models_neutral_snps/ELK_WHITE.no_mig.optimized.csv")

elk_white_no_mig_opt_results_clean <- elk_white_no_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

elk_white_mod1 <- ggplot(elk_white_no_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "NM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank())

#MODEL 2: SYM_MIG
elk_white_sym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/elk_white/diversification_models_neutral_snps/ELK_WHITE.sym_mig.optimized.csv")

elk_white_sym_mig_opt_results_clean <- elk_white_sym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

elk_white_mod2 <- ggplot(elk_white_sym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "SM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank()) + 
  theme(axis.title.y = element_blank())

#MODEL 3: ASYM_MIG
elk_white_asym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/elk_white/diversification_models_neutral_snps/ELK_WHITE.asym_mig.optimized.csv")

elk_white_asym_mig_opt_results_clean <- elk_white_asym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

elk_white_mod3 <- ggplot(elk_white_asym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "AM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank()) + 
  theme(axis.title.y = element_blank())

#MODEL 4: SEC_CONTACT_SYM_MIG
elk_white_sec_contact_sym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/elk_white/diversification_models_neutral_snps/ELK_WHITE.sec_contact_sym_mig.optimized.csv")

elk_white_sec_contact_sym_mig_opt_results_clean <- elk_white_sec_contact_sym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

elk_white_mod4 <- ggplot(elk_white_sec_contact_sym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "SCSM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank())

#MODEL 5: SEC_CONTACT_ASYM_MIG
elk_white_sec_contact_asym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/elk_white/diversification_models_neutral_snps/ELK_WHITE.sec_contact_asym_mig.optimized.csv")

elk_white_sec_contact_asym_mig_opt_results_clean <- elk_white_sec_contact_asym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

elk_white_mod5 <- ggplot(elk_white_sec_contact_asym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "SCAM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank()) + 
  theme(axis.title.y = element_blank())

#MODEL 6: ANC_SYM_MIG
elk_white_anc_sym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/elk_white/diversification_models_neutral_snps/ELK_WHITE.anc_sym_mig.optimized.csv")

elk_white_anc_sym_mig_opt_results_clean <- elk_white_anc_sym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

elk_white_mod6 <- ggplot(elk_white_anc_sym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "ASM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank()) + 
  theme(axis.title.y = element_blank())

#MODEL 7: ANC_ASYM_MIG
elk_white_anc_asym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/elk_white/diversification_models_neutral_snps/ELK_WHITE.anc_asym_mig.optimized.csv")

elk_white_anc_asym_mig_opt_results_clean <- elk_white_anc_asym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

elk_white_mod7 <- ggplot(elk_white_anc_asym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "AAM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey"))

#MODEL 8: SYM_MIG_TWOEPOCH
elk_white_sym_mig_twoepoc_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/elk_white/diversification_models_neutral_snps/ELK_WHITE.sym_mig_twoepoch.optimized.csv")

elk_white_sym_mig_twoepoch_opt_results_clean <- elk_white_sym_mig_twoepoc_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

elk_white_mod8 <- ggplot(elk_white_sym_mig_twoepoch_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "SM2E") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) + 
  theme(axis.title.y = element_blank())

#MODEL 9: ASYM_MIG_TWOEPOCH
elk_white_asym_mig_twoepoc_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/elk_white/diversification_models_neutral_snps/ELK_WHITE.asym_mig_twoepoch.optimized.csv")

elk_white_asym_mig_twoepoch_opt_results_clean <- elk_white_asym_mig_twoepoc_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

elk_white_mod9 <- ggplot(elk_white_asym_mig_twoepoch_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "AM2E") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) + 
  theme(axis.title.y = element_blank())

pdf("../../visualization/dadi_figures/dadi_optimizations/elk_white_optimizations.pdf", height = 20, width = 20)

plot_grid(elk_white_mod1, 
          elk_white_mod2, 
          elk_white_mod3, 
          elk_white_mod4, 
          elk_white_mod5, 
          elk_white_mod6, 
          elk_white_mod7, 
          elk_white_mod8, 
          elk_white_mod9,
          nrow = 3,
          ncol = 3, 
          labels = c("a","b","c","d","e","f","g","h","i"),
          label_size = 25,
          label_y = 1.02)

dev.off()
```

## BAYOU and WHITE 
```{r}
#MODEL 1: NO_MIG
bayou_white_no_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/bayou_white/diversification_models_neutral_snps/BAYOU_WHITE.no_mig.optimized.csv")

bayou_white_no_mig_opt_results_clean <- bayou_white_no_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

bayou_white_mod1 <- ggplot(bayou_white_no_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "NM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank())

#MODEL 2: SYM_MIG
bayou_white_sym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/bayou_white/diversification_models_neutral_snps/BAYOU_WHITE.sym_mig.optimized.csv")

bayou_white_sym_mig_opt_results_clean <- bayou_white_sym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

bayou_white_mod2 <- ggplot(bayou_white_sym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "SM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank()) + 
  theme(axis.title.y = element_blank())

#MODEL 3: ASYM_MIG
bayou_white_asym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/bayou_white/diversification_models_neutral_snps/BAYOU_WHITE.asym_mig.optimized.csv")

bayou_white_asym_mig_opt_results_clean <- bayou_white_asym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

bayou_white_mod3 <- ggplot(bayou_white_asym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "AM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank()) + 
  theme(axis.title.y = element_blank())

#MODEL 4: SEC_CONTACT_SYM_MIG
bayou_white_sec_contact_sym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/bayou_white/diversification_models_neutral_snps/BAYOU_WHITE.sec_contact_sym_mig.optimized.csv")

bayou_white_sec_contact_sym_mig_opt_results_clean <- bayou_white_sec_contact_sym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

bayou_white_mod4 <- ggplot(bayou_white_sec_contact_sym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "SCSM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank())

#MODEL 5: SEC_CONTACT_ASYM_MIG
bayou_white_sec_contact_asym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/bayou_white/diversification_models_neutral_snps/BAYOU_WHITE.sec_contact_asym_mig.optimized.csv")

bayou_white_sec_contact_asym_mig_opt_results_clean <- bayou_white_sec_contact_asym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

bayou_white_mod5 <- ggplot(bayou_white_sec_contact_asym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "SCAM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank()) + 
  theme(axis.title.y = element_blank())

#MODEL 6: ANC_SYM_MIG
bayou_white_anc_sym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/bayou_white/diversification_models_neutral_snps/BAYOU_WHITE.anc_sym_mig.optimized.csv")

bayou_white_anc_sym_mig_opt_results_clean <- bayou_white_anc_sym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

bayou_white_mod6 <- ggplot(bayou_white_anc_sym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "ASM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank()) + 
  theme(axis.title.y = element_blank())

#MODEL 7: ANC_ASYM_MIG
bayou_white_anc_asym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/bayou_white/diversification_models_neutral_snps/BAYOU_WHITE.anc_asym_mig.optimized.csv")

bayou_white_anc_asym_mig_opt_results_clean <- bayou_white_anc_asym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

bayou_white_mod7 <- ggplot(bayou_white_anc_asym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "AAM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey"))

#MODEL 8: SYM_MIG_TWOEPOCH
bayou_white_sym_mig_twoepoc_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/bayou_white/diversification_models_neutral_snps/BAYOU_WHITE.sym_mig_twoepoch.optimized.csv")

bayou_white_sym_mig_twoepoch_opt_results_clean <- bayou_white_sym_mig_twoepoc_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

bayou_white_mod8 <- ggplot(bayou_white_sym_mig_twoepoch_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "SM2E") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) + 
  theme(axis.title.y = element_blank())

#MODEL 9: ASYM_MIG_TWOEPOCH
bayou_white_asym_mig_twoepoc_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/bayou_white/diversification_models_neutral_snps/BAYOU_WHITE.asym_mig_twoepoch.optimized.csv")

bayou_white_asym_mig_twoepoch_opt_results_clean <- bayou_white_asym_mig_twoepoc_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

bayou_white_mod9 <- ggplot(bayou_white_asym_mig_twoepoch_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "AM2E") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) + 
  theme(axis.title.y = element_blank())

pdf("../../visualization/dadi_figures/dadi_optimizations/bayou_white_optimizations.pdf", height = 20, width = 20)

plot_grid(bayou_white_mod1, 
          bayou_white_mod2, 
          bayou_white_mod3, 
          bayou_white_mod4, 
          bayou_white_mod5, 
          bayou_white_mod6, 
          bayou_white_mod7, 
          bayou_white_mod8, 
          bayou_white_mod9,
          nrow = 3,
          ncol = 3, 
          labels = c("a","b","c","d","e","f","g","h","i"),
          label_size = 25,
          label_y = 1.02)

dev.off()
```

## UPPARK and WHITE 
```{r}
#MODEL 1: NO_MIG
uppark_white_no_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/uppark_white/diversification_models_neutral_snps/UPPARK_WHITE.no_mig.optimized.csv")

uppark_white_no_mig_opt_results_clean <- uppark_white_no_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

uppark_white_mod1 <- ggplot(uppark_white_no_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "NM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank())

#MODEL 2: SYM_MIG
uppark_white_sym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/uppark_white/diversification_models_neutral_snps/UPPARK_WHITE.sym_mig.optimized.csv")

uppark_white_sym_mig_opt_results_clean <- uppark_white_sym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

uppark_white_mod2 <- ggplot(uppark_white_sym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "SM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank()) + 
  theme(axis.title.y = element_blank())

#MODEL 3: ASYM_MIG
uppark_white_asym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/uppark_white/diversification_models_neutral_snps/UPPARK_WHITE.asym_mig.optimized.csv")

uppark_white_asym_mig_opt_results_clean <- uppark_white_asym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

uppark_white_mod3 <- ggplot(uppark_white_asym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "AM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank()) + 
  theme(axis.title.y = element_blank())

#MODEL 4: SEC_CONTACT_SYM_MIG
uppark_white_sec_contact_sym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/uppark_white/diversification_models_neutral_snps/UPPARK_WHITE.sec_contact_sym_mig.optimized.csv")

uppark_white_sec_contact_sym_mig_opt_results_clean <- uppark_white_sec_contact_sym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

uppark_white_mod4 <- ggplot(uppark_white_sec_contact_sym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "SCSM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank())

#MODEL 5: SEC_CONTACT_ASYM_MIG
uppark_white_sec_contact_asym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/uppark_white/diversification_models_neutral_snps/UPPARK_WHITE.sec_contact_asym_mig.optimized.csv")

uppark_white_sec_contact_asym_mig_opt_results_clean <- uppark_white_sec_contact_asym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

uppark_white_mod5 <- ggplot(uppark_white_sec_contact_asym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "SCAM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank()) + 
  theme(axis.title.y = element_blank())

#MODEL 6: ANC_SYM_MIG
uppark_white_anc_sym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/uppark_white/diversification_models_neutral_snps/UPPARK_WHITE.anc_sym_mig.optimized.csv")

uppark_white_anc_sym_mig_opt_results_clean <- uppark_white_anc_sym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

uppark_white_mod6 <- ggplot(uppark_white_anc_sym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "ASM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank()) + 
  theme(axis.title.y = element_blank())

#MODEL 7: ANC_ASYM_MIG
uppark_white_anc_asym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/uppark_white/diversification_models_neutral_snps/UPPARK_WHITE.anc_asym_mig.optimized.csv")

uppark_white_anc_asym_mig_opt_results_clean <- uppark_white_anc_asym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

uppark_white_mod7 <- ggplot(uppark_white_anc_asym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "AAM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey"))

#MODEL 8: SYM_MIG_TWOEPOCH
uppark_white_sym_mig_twoepoc_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/uppark_white/diversification_models_neutral_snps/UPPARK_WHITE.sym_mig_twoepoch.optimized.csv")

uppark_white_sym_mig_twoepoch_opt_results_clean <- uppark_white_sym_mig_twoepoc_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

uppark_white_mod8 <- ggplot(uppark_white_sym_mig_twoepoch_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "SM2E") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) + 
  theme(axis.title.y = element_blank())

#MODEL 9: ASYM_MIG_TWOEPOCH
uppark_white_asym_mig_twoepoc_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/uppark_white/diversification_models_neutral_snps/UPPARK_WHITE.asym_mig_twoepoch.optimized.csv")

uppark_white_asym_mig_twoepoch_opt_results_clean <- uppark_white_asym_mig_twoepoc_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

uppark_white_mod9 <- ggplot(uppark_white_asym_mig_twoepoch_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "AM2E") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) + 
  theme(axis.title.y = element_blank())

pdf("../../visualization/dadi_figures/dadi_optimizations/uppark_white_optimizations.pdf", height = 20, width = 20)

plot_grid(uppark_white_mod1, 
          uppark_white_mod2, 
          uppark_white_mod3, 
          uppark_white_mod4, 
          uppark_white_mod5, 
          uppark_white_mod6, 
          uppark_white_mod7, 
          uppark_white_mod8, 
          uppark_white_mod9,
          nrow = 3,
          ncol = 3, 
          labels = c("a","b","c","d","e","f","g","h","i"),
          label_size = 25,
          label_y = 1.02)

dev.off()
```

## ILLI and SKIA 
```{r}
#MODEL 1: NO_MIG
illi_skia_no_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/illi_skia/diversification_models_neutral_snps/ILLI_SKIA.no_mig.optimized.csv")

illi_skia_no_mig_opt_results_clean <- illi_skia_no_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

illi_skia_mod1 <- ggplot(illi_skia_no_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "NM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank())

#MODEL 2: SYM_MIG
illi_skia_sym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/illi_skia/diversification_models_neutral_snps/ILLI_SKIA.sym_mig.optimized.csv")

illi_skia_sym_mig_opt_results_clean <- illi_skia_sym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

illi_skia_mod2 <- ggplot(illi_skia_sym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "SM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank()) + 
  theme(axis.title.y = element_blank())

#MODEL 3: ASYM_MIG
illi_skia_asym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/illi_skia/diversification_models_neutral_snps/ILLI_SKIA.asym_mig.optimized.csv")

illi_skia_asym_mig_opt_results_clean <- illi_skia_asym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

illi_skia_mod3 <- ggplot(illi_skia_asym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "AM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank()) + 
  theme(axis.title.y = element_blank())

#MODEL 4: SEC_CONTACT_SYM_MIG
illi_skia_sec_contact_sym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/illi_skia/diversification_models_neutral_snps/ILLI_SKIA.sec_contact_sym_mig.optimized.csv")

illi_skia_sec_contact_sym_mig_opt_results_clean <- illi_skia_sec_contact_sym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

illi_skia_mod4 <- ggplot(illi_skia_sec_contact_sym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "SCSM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank())

#MODEL 5: SEC_CONTACT_ASYM_MIG
illi_skia_sec_contact_asym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/illi_skia/diversification_models_neutral_snps/ILLI_SKIA.sec_contact_asym_mig.optimized.csv")

illi_skia_sec_contact_asym_mig_opt_results_clean <- illi_skia_sec_contact_asym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

illi_skia_mod5 <- ggplot(illi_skia_sec_contact_asym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "SCAM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank()) + 
  theme(axis.title.y = element_blank())

#MODEL 6: ANC_SYM_MIG
illi_skia_anc_sym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/illi_skia/diversification_models_neutral_snps/ILLI_SKIA.anc_sym_mig.optimized.csv")

illi_skia_anc_sym_mig_opt_results_clean <- illi_skia_anc_sym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

illi_skia_mod6 <- ggplot(illi_skia_anc_sym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "ASM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) +
  theme(axis.title.x = element_blank()) + 
  theme(axis.title.y = element_blank())

#MODEL 7: ANC_ASYM_MIG
illi_skia_anc_asym_mig_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/illi_skia/diversification_models_neutral_snps/ILLI_SKIA.anc_asym_mig.optimized.csv")

illi_skia_anc_asym_mig_opt_results_clean <- illi_skia_anc_asym_mig_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

illi_skia_mod7 <- ggplot(illi_skia_anc_asym_mig_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "AAM") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey"))

#MODEL 8: SYM_MIG_TWOEPOCH
illi_skia_sym_mig_twoepoc_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/illi_skia/diversification_models_neutral_snps/ILLI_SKIA.sym_mig_twoepoch.optimized.csv")

illi_skia_sym_mig_twoepoch_opt_results_clean <- illi_skia_sym_mig_twoepoc_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

illi_skia_mod8 <- ggplot(illi_skia_sym_mig_twoepoch_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "SM2E") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) + 
  theme(axis.title.y = element_blank())

#MODEL 9: ASYM_MIG_TWOEPOCH
illi_skia_asym_mig_twoepoc_opt_results <- read_csv("../dadi_analysis/analysis/text_file_results/illi_skia/diversification_models_neutral_snps/ILLI_SKIA.asym_mig_twoepoch.optimized.csv")

illi_skia_asym_mig_twoepoch_opt_results_clean <- illi_skia_asym_mig_twoepoc_opt_results %>%
  mutate(Model = factor(Model),
         Round = factor(Round))

illi_skia_mod9 <- ggplot(illi_skia_asym_mig_twoepoch_opt_results_clean, aes(x = Round, y = log.likelihood, fill = Round)) + 
  geom_boxplot(show.legend = F, outlier.shape = NA, alpha = 0.6) +
  geom_point(position = position_jitter(width = 0.2), alpha = 0.6, color = "black", pch = 21, show.legend = F) +
  theme_set(theme_cowplot(12)) +
  labs(x = "Optimization Round", y = "Log-likelihood Score", title = "AM2E") +
  theme(axis.text = element_text(size = 15)) +
  theme(axis.title = element_text(size = 15)) +
  theme(plot.title = element_text(size = 20, hjust = 0.5)) +
  scale_fill_manual(values = c("grey","grey","grey","grey")) + 
  theme(axis.title.y = element_blank())

pdf("../../visualization/dadi_figures/dadi_optimizations/illi_skia_optimizations.pdf", height = 20, width = 20)

plot_grid(illi_skia_mod1, 
          illi_skia_mod2, 
          illi_skia_mod3, 
          illi_skia_mod4, 
          illi_skia_mod5, 
          illi_skia_mod6, 
          illi_skia_mod7, 
          illi_skia_mod8, 
          illi_skia_mod9,
          nrow = 3,
          ncol = 3, 
          labels = c("a","b","c","d","e","f","g","h","i"),
          label_size = 25,
          label_y = 1.02)

dev.off()
```
