---
title: "SMB_HYBRID_DETECTIVE"
author: "Joe Gunn"
date: "7/10/2020"
output: html_document
---

## Libraries needed for analysis
```{r}
library(genepopedit)
library(parallelnewhybrid)
library(hybriddetective)
library(readxl)
library(tidyverse)
library(graph4lg)
library(adegenet)
library(cowplot)
```

## Get top 200 diagnostic loci
```{r}
#Expore genepop data using genepopedit package
genepop_detective("../../raw_data/genepop_data/hsyc_white_pure_genepop.txt", variable = "PopNum")
genepop_detective("../../raw_data/genepop_data/hsyc_white_pure_genepop_2pop.txt", variable = "PopNum")
genepop_detective("../../raw_data/genepop_data/hsyc_skia_pure_genepop.txt", variable = "PopNum")
genepop_detective("../../raw_data/genepop_data/hsyc_skia_pure_genepop_2pop.txt", variable = "PopNum")
genepop_flatten("../../raw_data/genepop_data/hsyc_white_pure_genepop_biall_2pop.txt")
genepop_flatten("../../raw_data/genepop_data/hsyc_skia_pure_genepop.txt")
genepop_flatten("../../raw_data/genepop_data/hsyc_skia_pure_genepop_biall_2pop.txt")
genepop_flatten("../../../../../../hsyc_skia_200_panel_genepop_2pop_full.txt")
genepop_flatten("../../../../../../hsyc_white_200_panel_genepop_2pop_full.txt")
genepop_flatten("../../raw_data/genepop_data/hybrid_lab_simulations/text_files/hsyc_white_P1_P2_sim_2pop.txt")
genepop_detective("../../raw_data/genepop_data/hybrid_lab_simulations/text_files/hsyc_white_P1_P2_sim_2pop.txt", variable = "PopNum")
genepop_flatten("../../raw_data/genepop_data/hybrid_lab_simulations/text_files/hsyc_white_F1_HSYC_sim.txt")
genepop_detective("../../raw_data/genepop_data/hybrid_lab_simulations/text_files/hsyc_white_F1_HSYC_sim_2pop.txt", variable = "PopNum")
genepop_flatten("../../raw_data/genepop_data/hybrid_lab_simulations/text_files/hsyc_white_F1_WHITE_sim.txt")
genepop_flatten("../../raw_data/genepop_data/hybrid_lab_simulations/text_files/hsyc_skia_P1_P2_sim.txt")
genepop_detective("../../raw_data/genepop_data/hybrid_lab_simulations/text_files/hsyc_skia_F1_HSYC_sim_2pop.txt", variable = "PopNum")
genepop_detective("../../raw_data/genepop_data/hybrid_lab_simulations/text_files/hsyc_skia_F1_SKIA_sim_2pop.txt", variable = "PopNum")


#create a dataframe to designate two different populations (Pure Neosho, Pure Northern)
pop_rename_white <- data.frame(Opop = c("","","","","","","","","","","","","","","","","",""), Rename = c("HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE"))

pop_rename_skia <- data.frame(Opop = c("","","","","","","","","","","","",""), Rename = c("HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","SKIA","SKIA","SKIA","SKIA","SKIA"))

#Designate the two different populations (Pure Neosho, Pure Northern)
subset_genepop_rename("../../raw_data/genepop_data/hsyc_white_200_panel_genepop_full.txt", pop_rename_white, path = "/Users/joegunn/Desktop/hsyc_white_200_panel_genepop_2pop_full.txt")

subset_genepop_rename("../../raw_data/genepop_data/hsyc_skia_200_panel_genepop_full.txt", pop_rename_skia, path = "/Users/joegunn/Desktop/hsyc_skia_200_panel_genepop_2pop_full.txt")

#Run command to extract the top 200 diagnositic SNPs (with highest Fst values) across pure Neosho and Northern populations. Both PGDSpider and PLINK needed to be installed on my local computer, and the respective paths to both executables are given in this function. 

#Get panel SNP panel for Skiatook lake and Honey Syc populations
getTopLoc(GPD = "/Users/joegunn/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Genomics/raw_data/genepop_data/hsyc_skia_pure_genepop_biall_2pop.txt", panel.size = 200,
where.PGDspider = "/Users/joegunn/Downloads/PGDSpider_2.1.1.5/", where.PLINK = "/Users/joegunn/Downloads/plink_mac_20200616/")

#Get panel SNP panel for White and Honey Syc populations
getTopLoc(GPD = "/Users/joegunn/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Genomics/raw_data/genepop_data/hsyc_white_pure_genepop_biall_2pop.txt", panel.size = 200,
where.PGDspider = "/Users/joegunn/Downloads/PGDSpider_2.1.1.5/", where.PLINK = "/Users/joegunn/Downloads/plink_mac_20200616/")
```

## Determine the SNP names for the 200 diagnostic SNPs discovered in the above analyses - this is necessary, because the hybriddetective workflow code just generates the number of the SNPs that were used to make the panel (SNP_1, 2, 3, etc.) rather than the actual SNP name.
```{r}
snp_metadata <- read_excel("../../metadata/smb_snp_metadata.xlsx")
snp_metadata <- snp_metadata %>%
  mutate(snp_number = factor(snp_number))

#Honey Creek and Sycamore Creek with the White River SNPs
hsyc_white_200_panel_snps <- read_excel("../../metadata/hsyc_white_200_panel.xlsx")
hsyc_white_200_panel_snps <- hsyc_white_200_panel_snps %>%
  mutate(snp_number = factor(snp_number))

hsyc_white_200_panel_snp_names <- merge(snp_metadata, hsyc_white_200_panel_snps, by = "snp_number")

#Honey Creek and Sycamore Creek with Skiatook Lake SNPs
hsyc_skia_200_panel_snps <- read_excel("../../metadata/hsyc_skia_200_panel.xlsx")
hsyc_skia_200_panel_snps <- hsyc_skia_200_panel_snps %>%
  mutate(snp_number = factor(snp_number))

hsyc_skia_200_panel_snp_names <- merge(snp_metadata, hsyc_skia_200_panel_snps, by = "snp_number")

#Write out tables with SNP names to be kept for hybrid analysis - these will be text files that can be later used in vcftools to subset vcfs on Lewis 
write.table(hsyc_white_200_panel_snp_names,"~/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Genomics/metadata/hsyc_white_200_panel_snp_names.txt", sep="\t")

write.table(hsyc_skia_200_panel_snp_names,"~/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Genomics/metadata/hsyc_skia_200_panel_snp_names.txt", sep="\t")
```

## HYBRIDLAB ANALYSIS
### In the program HYBRIDLAB, I am simulating 6 hybrid categories (P1, P2, F1, F2, BC1, BC2) for hybrid populations between HSYC and WHITE and between HSYC and SKIA. I am generating 100 simulated individuals for each category, including simulated parent individuals, even though I have empirical data for the parents. This will allow me to assess all differences or similarities with equal sample sizes. Simulated genotypes will be compared to the individual admixed populations from my study

## Format simulated data files from HYBRIDLAB 
```{r}
#Format genepop file for simulated HSYC and WHITE parent 1 and 2 
pop_rename_hsyc_white_p1_p2 <- data.frame(Opop = c("","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","",""), Rename = c("P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2"))

subset_genepop_rename("../../raw_data/genepop_data/hybrid_lab_simulations/text_files/hsyc_white_P1_P2_sim.txt", pop_rename_hsyc_white_p1_p2, path = "/Users/joegunn/Desktop/hsyc_white_P1_P2_sim_2pop.txt")

#Format genepop file for simulated HSYC and WHITE F1 backcross to HSYC 
pop_rename_hsyc_white_F1_HSYC <- data.frame(Opop = c("","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","",""), Rename = c("HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1"))

subset_genepop_rename("../../raw_data/genepop_data/hybrid_lab_simulations/text_files/hsyc_white_F1_HSYC_sim.txt", pop_rename_hsyc_white_F1_HSYC, path = "/Users/joegunn/Desktop/hsyc_white_F1_HSYC_sim_2pop.txt")

#Format genepop file for simulated HSYC and WHITE F1 backcross to WHITE 
pop_rename_hsyc_white_F1_WHITE <- data.frame(Opop = c("","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","",""), Rename = c("WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1"))

subset_genepop_rename("../../raw_data/genepop_data/hybrid_lab_simulations/text_files/hsyc_white_F1_WHITE_sim.txt", pop_rename_hsyc_white_F1_WHITE, path = "/Users/joegunn/Desktop/hsyc_white_F1_WHITE_sim_2pop.txt")

#Format genepop file for simulated HSYC and SKIA parent 1 and 2 
pop_rename_hsyc_skia_p1_p2 <- data.frame(Opop = c("","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","",""), Rename = c("P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P1","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2","P2"))

subset_genepop_rename("../../raw_data/genepop_data/hybrid_lab_simulations/text_files/hsyc_skia_P1_P2_sim.txt", pop_rename_hsyc_skia_p1_p2, path = "/Users/joegunn/Desktop/hsyc_skia_P1_P2_sim_2pop.txt")

#Format genepop file for simulated HSYC and SKIA F1 backcross to HSYC 
pop_rename_hsyc_skia_F1_HSYC <- data.frame(Opop = c("","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","",""), Rename = c("HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1"))

subset_genepop_rename("../../raw_data/genepop_data/hybrid_lab_simulations/text_files/hsyc_skia_F1_HSYC_sim.txt", pop_rename_hsyc_skia_F1_HSYC, path = "/Users/joegunn/Desktop/hsyc_skia_F1_HSYC_sim_2pop.txt")

#Format genepop file for simulated HSYC and SKIA F1 backcross to SKIA 
pop_rename_hsyc_skia_F1_SKIA <- data.frame(Opop = c("","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","","",""), Rename = c("SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","SKIA","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1","F1"))

subset_genepop_rename("../../raw_data/genepop_data/hybrid_lab_simulations/text_files/hsyc_skia_F1_SKIA_sim.txt", pop_rename_hsyc_skia_F1_SKIA, path = "/Users/joegunn/Desktop/hsyc_skia_F1_SKIA_sim_2pop.txt")
```

## Format all hybrid datafiles
```{r}
##WHITE RIVER ADMIXED POPS
pop_rename_white_bayou <- data.frame(Opop = c("","","","","","","","","","","","","","","","","","","","","","",""), Rename = c("AT","AT","AT","AT","AT","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE"))

subset_genepop_rename("../../raw_data/genepop_data/hsyc_white_admixed_vcf/hsyc_white_BAYOU_genepop.txt", pop_rename_white_bayou, path = "/Users/joegunn/Desktop/hsyc_white_BAYOU_genepop_correct.txt")


pop_rename_white_bsug <- data.frame(Opop = c("","","","","","","","","","","","","","","","","","","","","","","",""), Rename = c("MI","MI","MI","MI","MI","MI","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE"))

subset_genepop_rename("../../raw_data/genepop_data/hsyc_white_admixed_vcf/hsyc_white_BSUG_genepop.txt", pop_rename_white_bsug, path = "/Users/joegunn/Desktop/hsyc_white_BSUG_genepop_correct.txt")


pop_rename_white_buff <- data.frame(Opop = c("","","","","","","","","","","","","","","","","","","","","","","",""), Rename = c("BC","BC","BC","BC","BC","BC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE"))

subset_genepop_rename("../../raw_data/genepop_data/hsyc_white_admixed_vcf/hsyc_white_BUFF_genepop.txt", pop_rename_white_buff, path = "/Users/joegunn/Desktop/hsyc_white_BUFF_genepop_correct.txt")


pop_rename_white_elk <- data.frame(Opop = c("","","","","","","","","","","","","","","","","","","","","","","",""), Rename = c("ELK","ELK","ELK","ELK","ELK","ELK","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE"))

subset_genepop_rename("../../raw_data/genepop_data/hsyc_white_admixed_vcf/hsyc_white_ELK_genepop.txt", pop_rename_white_elk, path = "/Users/joegunn/Desktop/hsyc_white_ELK_genepop_correct.txt")


pop_rename_white_spav <- data.frame(Opop = c("","","","","","","","","","","","","","","","","","","","","","","",""), Rename = c("SPVW","SPVW","SPVW","SPVW","SPVW","SPVW","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE","WHITE"))

subset_genepop_rename("../../raw_data/genepop_data/hsyc_white_admixed_vcf/hsyc_white_SPAV_genepop.txt", pop_rename_white_spav, path = "/Users/joegunn/Desktop/hsyc_white_SPAV_genepop_correct.txt")



#SKIATOOK LAKE ADMIXED POPS
pop_rename_skia_baron <- data.frame(Opop = c("","","","","","","","","","","","","","","","","",""), Rename = c("BFORK","BFORK","BFORK","BFORK","BFORK","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","SKIA","SKIA","SKIA","SKIA","SKIA"))

subset_genepop_rename("../../raw_data/genepop_data/hsyc_skia_admixed_vcf/hsyc_skia_BARON_genepop.txt", pop_rename_skia_baron, path = "/Users/joegunn/Desktop/hsyc_skia_BARON_genepop_correct.txt")


pop_rename_skia_caney <- data.frame(Opop = c("","","","","","","","","","","","","","","","","",""), Rename = c("CANEY","CANEY","CANEY","CANEY","CANEY","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","SKIA","SKIA","SKIA","SKIA","SKIA"))

subset_genepop_rename("../../raw_data/genepop_data/hsyc_skia_admixed_vcf/hsyc_skia_CANEY_genepop.txt", pop_rename_skia_caney, path = "/Users/joegunn/Desktop/hsyc_skia_CANEY_genepop_correct.txt")


pop_rename_skia_illinois <- data.frame(Opop = c("","","","","","","","","","","","","","","","","","","",""), Rename = c("ILLINOIS","ILLINOIS","ILLINOIS","ILLINOIS","ILLINOIS","ILLINOIS","ILLINOIS","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","HSYC","SKIA","SKIA","SKIA","SKIA","SKIA"))

subset_genepop_rename("../../raw_data/genepop_data/hsyc_skia_admixed_vcf/hsyc_skia_ILLINOIS_genepop.txt", pop_rename_skia_illinois, path = "/Users/joegunn/Desktop/hsyc_skia_ILLINOIS_genepop_correct.txt")


genepop_flatten("../../../../../../hsyc_skia_ILLINOIS_genepop_correct.txt")
genepop_detective("../../../../../../hsyc_skia_ILLINOIS_genepop_correct.txt", variable = "PopNum")
```

```{r}

hsyc_skia_all_admix_genepop <- read_excel("../../raw_data/genepop_data/hybrid_lab_simulations/hybrid_category_genotypes/hsyc_skia/HSYC_SKIA_all_hybrids_allADMIX.xlsx")

admix_pops <- factor(c(rep("HSYC", times = 100), rep("SKIA", times = 100), rep("F1", times = 100), rep("F2", times = 100), rep("BC_HSYC", times = 100), rep("BC_SKIA", times = 100), rep("BARON", times = 5), rep("CANEY", times = 5), rep("ILLINOIS", times = 7)))

hsyc_skia_all_admix_genepop <- column_to_rownames(hsyc_skia_all_admix_genepop, "ind")
hsyc_skia_all_admix_genepop <- as.matrix(hsyc_skia_all_admix_genepop)

hsyc_skia_all_admix_genepop_genind <- df2genind(hsyc_skia_all_admix_genepop, 
                                                ncode = 3, 
                                                pop = admix_pops, 
                                                ploidy = 2)

hsyc_skia_all_admix_genepop_genind <- scaleGen(hsyc_skia_all_admix_genepop_genind, 
                                           center = TRUE, 
                                           scale = TRUE, 
                                           NA.method = c("mean"), 
                                           truenames = TRUE)

dapc_hsyc_skia_admix <- dapc(hsyc_skia_all_admix_genepop_genind, admix_pops)

scatter(dapc_hsyc_skia_admix)


hsyc_white_all_admix_genepop <- read_excel("../../raw_data/genepop_data/hybrid_lab_simulations/hybrid_category_genotypes/hsyc_white/HSYC_WHITE_all_hybrids_allADMIX.xlsx")

admix_pops_white <- factor(c(rep("HSYC", times = 100), rep("WHITE", times = 100), rep("F1", times = 100), rep("F2", times = 100), rep("BC_HSYC", times = 100), rep("BC_WHITE", times = 100), rep("BAYOU", times = 5), rep("BSUG", times = 6), rep("BUFF", times = 6), rep("ELK", times = 6), rep("SPVW", times = 6)))

hsyc_white_all_admix_genepop <- column_to_rownames(hsyc_white_all_admix_genepop, "ind")
hsyc_white_all_admix_genepop <- as.matrix(hsyc_white_all_admix_genepop)

hsyc_white_all_admix_genepop_genind <- df2genind(hsyc_white_all_admix_genepop, 
                                                 ncode = 3, 
                                                 pop = admix_pops_white, 
                                                 ploidy = 2)

hsyc_white_all_admix_genepop_genind <- scaleGen(hsyc_white_all_admix_genepop_genind, 
                                           center = TRUE, 
                                           scale = TRUE, 
                                           NA.method = c("mean"), 
                                           truenames = TRUE)

dapc_hsyc_white_admix <- dapc(hsyc_white_all_admix_genepop_genind, admix_pops_white)

scatter(dapc_hsyc_white_admix)

## HSYC SKIA Plot
dapc_hsyc_skia_admix_LDs <- as.data.frame(dapc_hsyc_skia_admix$ind.coord)
dapc_hsyc_skia_admix_LDs <- cbind(data.frame(admix_pops), dapc_hsyc_skia_admix_LDs)
colnames(dapc_hsyc_skia_admix_LDs) <- c("pop","LD1","LD2")

dapc_hsyc_skia_admix_plot <- ggplot(dapc_hsyc_skia_admix_LDs, aes(x = LD1, y = LD2, fill = pop)) +
   geom_point(aes(fill = pop), color = "black", pch = 21, size = 5, show.legend = T) +
   labs(x = "LD1", y = "LD2", fill = "Population") +
   scale_fill_manual(values = c("turquoise", "grey44","grey100", "firebrick3","grey84","grey64","deepskyblue","mediumpurple","navyblue", "deeppink2")) +
   theme_set(theme_cowplot(12)) +
   theme(legend.title = element_text(size = 20)) +
   theme(legend.title = element_text(face = "bold")) +
   theme(legend.text = element_text(size = 15)) +
   theme(legend.position = c(0.7,0.7)) +
   theme(legend.background = element_rect(color = "black", size = 0.5)) + 
   theme(legend.margin = margin(5, 5, 5, 5)) +
   theme(axis.title = element_text(size = 20)) +
   theme(axis.text = element_text(size = 20))

## HSYC WHITE Plot
dapc_hsyc_white_admix_LDs <- as.data.frame(dapc_hsyc_white_admix$ind.coord)
dapc_hsyc_white_admix_LDs <- cbind(data.frame(admix_pops_white), dapc_hsyc_white_admix_LDs)
colnames(dapc_hsyc_white_admix_LDs) <- c("pop","LD1","LD2")

dapc_hsyc_white_admix_plot <- ggplot(dapc_hsyc_white_admix_LDs, aes(x = LD1, y = LD2, fill = pop)) +
   geom_point(aes(fill = pop), color = "black", pch = 21, size = 5, show.legend = T) +
   labs(x = "LD1", y = "LD2", fill = "Population") +
   scale_fill_manual(values = c("lightgreen", "grey44","grey100", "sienna4", "lightyellow","lightsalmon","grey84","grey64","deepskyblue","orchid1", "deeppink2")) +
   theme_set(theme_cowplot(12)) +
   theme(legend.title = element_text(size = 20)) +
   theme(legend.title = element_text(face = "bold")) +
   theme(legend.text = element_text(size = 15)) +
   theme(legend.position = c(0.7,0.7)) +
   theme(legend.background = element_rect(color = "black", size = 0.5)) + 
   theme(legend.margin = margin(5, 5, 5, 5)) +
   theme(axis.title = element_text(size = 20)) +
   theme(axis.text = element_text(size = 20)) +
   theme(axis.text.x = element_blank()) +
   theme(axis.title.x = element_blank())


pdf("/Users/joegunn/Desktop/Grad_School_Stuff/Research/Projects/Smallmouth_Bass_Genomics/visualization/hybrid_detective/hyb_simulation_plots.pdf", width=9, height=12)

plot_grid(dapc_hsyc_white_admix_plot, dapc_hsyc_skia_admix_plot, nrow = 2, labels = c("a","b"), label_size = 27)

dev.off()
```
